---
title: "Testing the generality of host-symbiont cophylogeny"
subtitle: Electronic Supplementary Material
author: "Alexander Hayward, Robert Poulin & Shinichi Nakagawa"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: 
    toc: true # show a table of contents
    toc_float: true # make table of contents float at the side of the page
    depth: 3  # upto three depths of headings (specified by #, ## and ###)
    number_sections: false  # set to true if you want to number sections at each table header
    theme: lumen # nice fonts and colours
    code_folding: hide # Add some buttons to show/hide the code
#bibliography: bib.bib
---

<!--- Try to add references for this!!!! --->

## Setups

### Loading pacakges and custum functions

```{r setup, results='hide'}
# kniter seetting
knitr::opts_chunk$set(
	#message = FALSE, 
	#warning = FALSE, # no warnings
	tidy = TRUE,
	fig.width = 9
)
# clearning up
rm(list=ls())

# loading packages
pacman::p_load(tidyverse, # tidy family and related pacakges below
               kableExtra, 
               gridExtra, 
               purrr, 
               magrittr, # extending piping
               pander,   # nice tables
               metafor, # package for meta-analysis
               MCMCglmm # Bayeisan mixed model software
               )

# getting functions 
source("../R/funct.R", chdir = TRUE)
```


## Methodological details



### Dataset description

### Sample sizes

### Missing data

### Explorative analysis???

### Justification of the use of combined datasets....

## Results

### Publication bias and sensitivity analysis

### Recommendation
* they need to run more simuations so they do not max out!
* reanalysis of earlier trees are necessary; getting older or updated trees are required
* new studies should provide all data avaiable online so that future analysis can incorprate all avaiable data

## Acknowledgement

Much of coding materials have been borrowed from h

## Information for this R session

```{r session}
sessionInfo() %>% pander()
```
